Security Properties for Stack Safety

### 2021-05-14 short/main.tex
another stab at problematic paras

This formulation not only captures the intuition
that the callee cannot directly access the caller's state; it also gives a novel
interpretation of integrity and confidentiality in the presence of control-flow
attacks. The key is that every call has a corresponding predicate on states
designated a ``return target''
that defines what it means for that call to truly return. The program counter
must be at the next instruction, and the stack pointer restored to its original
value. A callee may execute the instructions of a return,
but if it does not reach a return target, we simply do not recognize it as a return.
So the callee can be ``active'', and the caller protected, even if the callee is
executing instructions that look like they belong to the caller.

Our attacker model is strong, allowing the attacker to execute arbitrary code, so
the callee has no reason to execute the caller's instructions -- any instruction it could
jump to, it could already execute. The only reason to perform a ``fake'' return in this setting
would be to access the caller's data, which our properties will correctly identify as a violation.

>>>>

\apt{Here's another stab:}
Our attacker model is very strong, allowing the attacker to execute arbitrary code.
In particular, we do not attempt to prevent \apt{most forms of?} control-flow attacks
\apt{such as ROP?}. The notions of integrity and confidentiality remain useful even
in the absence of normal control flow.
%This formulation not only captures the intuition
%that the callee cannot directly access the caller's state; it also gives a novel
%interpretation of integrity and confidentiality in the presence of control-flow
%attacks.
The key is that every call has a corresponding predicate on states
designated a ``return target''
that defines what it means for that call to truly return: the program counter
must be at the next instruction, and the stack pointer restored to its original
value. A callee may execute the instructions of a return,
but if it does not reach a return target, we simply do not recognize it as a return.
So the callee can be ``active'', and the caller protected, even if the callee is
executing instructions that look like they belong to the caller.

%Our attacker model is strong, allowing the attacker to execute arbitrary code, so
%the callee has no reason to execute the caller's instructions -- any instruction it could
%jump to, it could already execute. The only reason to perform a ``fake'' return in this setting
%would be to access the caller's data, which our properties will correctly identify as a violation.
